---
title: "Statistical Inference - Simulation"
author: "Ajani Gyasi"
date: '`r format(Sys.time(), ''%d %B, %Y'')`'
output: html_document
---





```{r required packages, echo=FALSE}
require('knitr', quietly = TRUE)
```
##Overview
In this project, we will examine whether an exponential distribution is comparable to the Central Limit Theorem. The exponential distribution will simulate 1000 trails with a sample size of 40, while a lambda rate is set to 0.2. As we investigate the distribution of averages, we will conclude whether its comparability satifies the Central Limit Theorem.

##Simulations 
We are doing a thousand simulations of the average (**means**) of 40 samples drawn from the exponential distribution.

```{r simulations}
sim <- 1000 #number of simulations
lambda <- 0.2 #lambda rate
n <- 40 #number of samples
m_exp <- 1/lambda #exponential mean
sd_exp <- 1/lambda #exponential standard deviation


set.seed(348) #seed for reporoducibility
dat_simulation <- matrix(rexp(n * sim, lambda), sim) #calculation
means <- rowMeans(dat_simulation) #simulation
```


##Sample Mean vs. Theoretical Mean
The sample mean or the simulated mean is 5.035, while the theoretical mean is 5. Notice, that this gives us a close estimate of the population mean.
```{r mean, echo=FALSE}
sample_mean <- round(mean(means), 3)
print(paste("Sample mean:", sample_mean))
theor_mean <- m_exp
print(paste("Theoretical mean:", theor_mean))
```

##Sample Variance vs. Theoretical Variance
The sample variance or the simulated variance is 0.634, while the theoretical variance is 0.625. Again, these numbers are fairly close.
```{r variance, echo=FALSE}
sample_var <- round(var(means), 3)
print(paste("Sample variance:", sample_var))
theor_var <- (sd_exp)^2/n
print(paste("Theoretical variance:", theor_var))
```


##Distribution 
The diagrams below showcase the exponential distribution being approximately normal. The Central Limit Theorem tells us that the averages of samples will follow a normal distribution. The two histograms prove the sample density follows a normal distribution. The qqplot double checks whether our simulation is in agreeance with the Central Limit Theorem.


```{r , echo=FALSE}
hist(means, breaks = 25, probability = TRUE, xlab = "", main = "Distribution of sample averages", col = "wheat")
lines(density(means), col = "green", lwd = 2) #simulation sample averages 
abline(v=m_exp, col = "red", lwd = 2) #Theoretical center of distribution
#Theoretical density of sample averages
curve(dnorm(x, m_exp, sd_exp/sqrt(n)), min(means), max(means), add = TRUE, col = "purple", lty = 2, lwd = 2)
legend("topright", c("simulation density", "theoretical density","theoretical mean"),bty = "n", lty = c(1,2,1), col = c("green", "purple", "red"))

library(ggplot2)
data <- data.frame(means)
normal <- ggplot(data, aes(x = means)) + geom_histogram(aes(y = ..density..), col = "grey", fill = "beige") 
normal + geom_density(aes(col = "purple"))

qqnorm(means)
qqline(means)
```